%
% File acl2016.tex
%
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}

\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B{\sc ib}\TeX}

\title{Instructions for ACL-2016 Proceedings}

\author{Tom Byars, Cale Clark, Roman Fenlon, Charlie Lyttle, Katie McAskill, Jack Miller, Zein Said, \\
{\bf Abdullah Sayed, Laura Schauer, Jason Sweeney, Aron Szeles, Xander Wickham} \\
School of Mathematics and Computer Science, Heriot-Watt University, Edinburgh \\ {\tt {tjb10, cc164, rf104, cl157, klm12, jjm7, zs2008,}} \\ {\tt {as512, lms9, js418, as472, aw127}@hw.ac.uk}}

\date{February 2023}

\begin{document}
\maketitle
\begin{abstract}
  This document contains the instructions for preparing a camera-ready
  manuscript for the proceedings of ACL-2016. The document itself
  conforms to its own specifications, and is therefore an example of
  what your manuscript should look like. These instructions should be
  used for both papers submitted for review and for final versions of
  accepted papers.  Authors are asked to conform to all the directions
  reported in this document. \cite{ACM:83}
\end{abstract}


\section{Introduction}
\label{sec:introduction}

This should be a 6-8 page conference paper with appendices, if relevant. 
\textit{from coursework spec:} main research or technical question addressed


\section{Background}
\label{sec:background}

\textit{from coursework spec:} literature review / related work, including a critical analysis of the field, and commentary on applicability of the technologies and methods used in emerging technologies and application areas


\section{Design and Implementation}
\label{sec:implementation}

\textit{from coursework spec:} design and implementation of the system: components and architecture


\section{Evaluation}
\label{sec:evaluation}

\textit{from coursework spec:} evaluation of the system and presentation of the results


\section{Future Work}
\label{sec:future_work}

\textit{from coursework spec:} suggestions for future work


\section*{Acknowledgments}
\label{sec:acknowledgments}

The acknowledgments should go immediately before the references.  Do
not number the acknowledgments section. Do not include this section
when submitting your paper for review.

% include your own bib file like this:
%\bibliographystyle{acl}
%\bibliography{acl2016}
\bibliography{acl2016}
\bibliographystyle{acl2016}

\appendix

\section{Supplemental Material, Appendix}
\label{sec:supplemental}


\end{document}
